\begin{center}
\begin{longtable}{| p{.2\textwidth} | p{.8\textwidth} |}
\caption{ICCMA 2017 Submissions}
\label{table:ICCMA2017Submissions}\\

\hline \multicolumn{1}{|c|}{\textbf{Solver}} & \multicolumn{1}{c|}{\textbf{Author}}\\ \hline 
\endfirsthead


\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Solver}} &
\multicolumn{1}{c|}{\textbf{Author}} \\ \hline 
\endhead

\hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

argmat-clpb   & Fuan Pu (Tsinghua University, China), Guiming Luo (Tsinghua University, China), Yucheng Chen (Tsinghua University, China).                  \\ \midrule
argmat-dvisat & Fuan Pu (Tsinghua University, China), Guiming Luo (Tsinghua University, China), Ya Hang (Tsinghua University, China).                    \\ \hline
argmat-mpg & Fuan Pu (Tsinghua University, China), Guiming Luo (Tsinghua University, China), Ya Hang (Tsinghua University, China).                    \\ \hline
argmat-sat & Fuan Pu (Tsinghua University, China), Guiming Luo (Tsinghua University, China), Ya Hang (Tsinghua University, China).                    \\ \hline
ArgSemSAT  & Federico Cerutti (Cardiff University, UK), Mauro Vallati (University of Huddersfield, UK), Massimiliano Giacomin (University of Brescia, Italy), Tobia Zanetti (University of Brescia, Italy). \\ \hline
ArgTools   & Samer Nofal (German Jordanian University, Jordan), Katie Atkinson (University of Liverpool, UK), Paul E. Dunne (University of Liverpool, UK).              \\ \hline
ASPrMin    & Wolfgang Faber (University of Huddersfield, UK), Mauro Vallati (University of Huddersfield, UK), Federico Cerutti (Cardiff University, UK), Massimiliano Giacomin (University of Brescia, Italy). \\ \hline
cegartix   & Wolfgang Dvořák (TU Wien, Austria), Matti Järvisalo (University of Helsinki, Finland), Johannes P. Wallner (TU Wien, Austria).                 \\ \hline
Chimærarg  & Federico Cerutti (Cardiff University, UK), Mauro Vallati (University of Huddersfield, UK), Massimiliano Giacomin (University of Brescia, Italy).              \\ \hline
ConArg  & Stefano Bistarelli (Università di Perugia, Italy), Fabio Rossi (Università di Perugia, Italy), Francesco Santini (Università di Perugia, Italy).              \\ \hline
CoQuiAAS   & Jean-Marie Lagniez (Univ. Artois, France), Emmanuel Lonca (Univ. Artois, France), Jean-Guy Mailly (Univ. Paris Descartes, France).                \\ \hline
EqArgSolver   & Odinaldo Rodrigues (King's College London, UK).                                       \\ \hline
gg-sts  & Tomi Jahunen (Aalto University, Finland), Shahab Tasharrofi (Aalto University, Finland).                            \\ \hline
goDIAMOND  & Stefan Ellmauthaler (Leipzig University, Germany), Hannes Strass (Leipzig University, Germany).                           \\ \hline
heureka    & Nils Geilen (Universität Koblenz-Landau, Germany), Matthias Thimm (Universität Koblenz-Landau, Germany).                        \\ \hline
pyglaf  & Mario Alviano (University of Calabria, Italy).                                       
\end{longtable}
\end{center}
